Transformation of forecasts for evaluating predictive performance in an epidemiological context

### 2023-04-27 reply_to_reviews.tex

In this manuscript the authors investigate how common scoring rules for probabilistic forecasts can be adjusted by transforming observed data and forecast predictions prior to scoring. They provide three clear motivations for applying such transformations prior to scoring, assess the implications of different transformations in great detail, and evaluate the effects of these transformations using real-world COVID-19 forecasts obtained from the European Forecast Hub. Approaches that can help us improve how we measure the utility of epidemic forecasts for decision-makers are definitely needed. This is a very nice and timely contribution to epidemic forecast evaluation, and I only have a few comments.

\blue
1. Line 96, typo: "log-transformtation".

\red
2. Figure 3: out of curiosity, do the rankings of forecasts A and B first switch at the same observed value (somewhere around 7?) in both panels? Zooming in, it looks as though maybe the switch occurs very slightly earlier for the log-transformed scoring.

3. Section 3.2, page 9: remarks concerning Figure 4 refer to months (e.g., May, July) but it's a little difficult to relate them to the figure, because the x-axis only has 6-month breaks and spans two years, so it isn't immediately apparent which year (or both?) the reader should focus on. That being said, it's great to see how the log-transformation yields similar scores when the forecasts miss peaks and troughs.

\blue
4. Line 281: missing closing parenthesis, "(or $\beta_{\sqrt{}} = 0$, respectively".

\red
5. Figure 7: I can appreciate that the correlation between the natural and logarithmic scores decreases over the forecast horizon, as the absolute forecast error grows. But I found panel B more challenging to interpret. I gather the key message is that model rankings are quite consistent between the natural and log scales (panel A) even though the absolute scores differ markedly between the two scales — an effect that increases over the forecast horizon (panel B). Perhaps adding a sentence to this effect in the accompanying text (lines 292-295) would help other readers to avoid my confusion.

\blue
6. Line 296, typo: "Figure Figure 8 shows ...".

\red
7. Section 3.4, page 14 and Figure 8: it's a welcome outcome that the Hub ensemble forecast remained the top model, given that the log-transformation clearly affects the individual model rankings. Presumably it would be reasonable to expect that ensemble forecasts for other regions, pathogens, etc, should be the best (or near-best) model when using log-transformed case counts?

8. Lines 327-329: "A potential downside is that forecast evaluation is unreliable in situations where observed values are zero or very small."

I feel there's an argument to be made here that rather than being a potential limitations, it could be considered an accurate reflection of the inherent uncertainty about the future course of an epidemic when case numbers are very small. This transformation also provides a valuable benefit in these situations, as the authors note a few sentences later: "It also gives higher weight to another type of situation one may care about, namely one in which numbers start to rise from a previously low level". This neatly illustrates the importance (as highlighted by the authors in this manuscript) of using multiple scoring rules to evaluate and compare forecasts.

9. Table SI.2, "Criteria for removing forecasts": forecasts were removed if their median prediction differed greatly from the true value. This should probably be mentioned in the manuscript text, somewhere around line 235 (where Table SI.2 is referenced), to notify the reader that the definition of "erroneous forecasts" includes forecasts that are in extremely poor agreement with the ground truth. Otherwise, I feel that "erroneous" may be open to misinterpretation (e.g., only removing forecasts that predicted negative counts, NaN values, etc).

\end{document}
